\begin{thebibliography}{99}
\bibitem{AM04} R. Alur and P. Madhusudan, Visibly pushdown languages,
36th ACM Symp. Theory of Computing (STOC 2004).

\bibitem{BCJ18} R. Bloem, K. Chatterjee and B. Jobstmann, Graph Games and Reactive Synthesis,
E. M. Clarke et al. (eds.), Handbook of Model Checking, Chapter 27, 921--962, Springer, 2018.

\bibitem{BDMSS11} % [8] of WRA
M. Boja\'{n}czyk, C. David, A. Muscholl, T. Schwentick and L. Segoufin,
Two-variable logic on data words,
ACM Trans. Computational Logic 12(4), 2011.

\bibitem{BKL14}
M. Boja\'{n}czyk, B. Klin, S. Lasota,
Automata theory in nominal sets,
Logical Methods in Computer Science, 10(3:4), 1--44, 2014.

\bibitem{BCGK12}
B. Bollig, A. Cyriac, P. Gastin and K. N. Kumar,
Model checking languages of data words,
15th Int. Conf. Foundations of Software Science and Computation Structures
(FoSSaCS 2012), 391--405. %, 2012.

\bibitem{BEM97}
A. Bouajjani, J. Esparza and O. Maler,
Reachability analysis of pushdown automata: Application to model-checking,
%CONCUR 1997,
8th Int. Conf. on Concurrency Theory (CONCUR 1997),
135--150.
%, 1997,
%https://doi.org/10.1007/3-540-63141-0\_10.

\bibitem{Bo02} % [11] of WRA
P. Bouyer,
A logical characterization of data languages,
Inform. Process. Lett. 84(2), 75--85, 2002.

\bibitem{BL69} J. R. B\"{u}chi and L. H. Landweber, Solving sequential conditions by finite-state strategies,
Trans. American Mathematical Society 138, 295--311, 1969.

\bibitem{CLTW17}
Y-F. Chen, O. Leng\'{a}l, T. Tan and Z. Wu,
Register automata with linear arithmetic,
32nd Annual ACM/IEEE Symp. on Logic in Computer Science (LICS 2017).

\bibitem{CK98} % [2]
E. Y. C. Cheng and M. Kaminski,
Context-free languages over infinite alphabets,
Acta Informatica 35, 245--267, 1998.

\bibitem{CGP01}
E. M. Clarke, O. Grumberg and D. A. Peled, Model checking. MIT Press, 2001.
%2017.

\bibitem{CL15}
L. Clemente and S Lasota,
Reachability analysis of first-order definable pushdown systems,
24th EACSL Annual Conf. on Computer Science Logic (CSL 2015), 244--259. %, 2015.

\bibitem{DFSS19}
L. D'Antoni, T. Ferreira, M. Sammartino and A. Silva,
Symbolic register automata,
31th Int. Conf. on Computer Aided Verification (CAV 2019).
%LNCS 11561, 2019.

\bibitem{DL09} % [3] %% [16] of RPQd
S. Demri and R. Lazi\'{c},
LTL with freeze quantifier and register automata,
ACM Trans. on Computational Logic 10(3), 2009.

\bibitem{DLN07} % [17] of RPQd
S. Demri, R. Lazi\'{c} and D. Nowak,
On the freeze quantifier in constraint LTL: Decidability and complexity,
Inform. Comput. 205(1), 2--24, 2007.

\bibitem{ESK14} R. Ehlers, S. A. Seshia and H. Kress-Gazit, Synthesis with identifiers,
15th Int. Conf. on Verification, Model Checking, and Abstract Interpretation (VMCAI 2014), 415--433.

\bibitem{EHRS00}
J. Esparza, D. Hansel, P. Rossmanith and S. Schwoon,
Efficient algorithms for model checking pushdown systems,
%CAV 2000,
12th Int. Conf. on Computer Aided Verification (CAV 2000), 232--247. %, 2000.

\bibitem{EKS01}
J. Esparza, A. Ku\v{c}era, S. Schwoon,
Model checking LTL with regular valuations for pushdown systems,
Inform. and Comput, 186(2), 355--376, 2003.

\bibitem{EFR19} L. Exibard, E. Filiot and P.-A. Reynier, Synthesis of data word transducers,
30th Int. Conf. on Concurrency Theory (CONCUR 2019).

\bibitem{Gr67}
S. A. Greibach,
A note on pushdown store automata and regular systems,
Proc. the American Mathematical Society 18, 263--268, 1967.

\bibitem{KF94} % [4]
M. Kaminski and N. Francez,
Finite-memory automata,
Theoret. Comput. Sci. 134, 322--363, 1994.

\bibitem{KK19} A. Khalimov and O. Kupferman, Register-bounded synthesis,
30th Int. Conf. on Concurrency Theory (CONCUR 2019).

\bibitem{KMB18} A. Khalimov, B. Maderbacher and R. Bloem, Bounded synthesis of register transducers,
16th Int Symp on Automated Technology for Verification and Analysis (ATVA 2018), 494--510.

\bibitem{LTV15} % [7]
L. Libkin, T. Tan and D. Vrgo\v{c},
Regular expressions for data words,
J. Computer and System Sciences 81(7), 1278--1297, 2015.

\bibitem{LV12} % [8]
L. Libkin and D. Vrgo\v{c},
Regular path queries on graphs with data,
15th Int. Conf. on Database Theory (ICDT 2012), 74--85.

\bibitem{MRT17}
A. S. Murawski, S. J. Ramsay and N. Tzevelekos:
Reachability in pushdown register automata,
J. Computer and System Sciences 87, 58--83, 2017.

\bibitem{NSV04} % [28] of WRA
F. Neven, T. Schwentick and V. Vianu,
Finite state machines for strings over infinite alphabets,
ACM Trans. on Computational Logic 5(3), 403--435, 2004.

\bibitem{PR89} A. Pnueli and R. Rosner, On the synthesis of a reactive module,
16th ACM Symp. on Principles of Programming Languages (POPL 1989), 179--190.

\bibitem{RBB10}
J. Rot, F. de Boer and M. Bonsangue,
Pushdown system representation for unbounded object creation,
Tech. Rep. KIT-13, Karlsruhe Institute of Technology, 38--52, 2010.

\bibitem{Se06} % [10] %% [40] of RPQd
L. Segoufin,
Automata and logics for words and trees over an infinite alphabet,
15th EACSL Annual Conf. on Computer Science Logic (CSL 2006), 41--57.

\bibitem{STS18} R. Senda, Y. Takata and H. Seki,
Complexity results on register context-free grammars and register tree automata,
%ICTAC 2018,
Int. Colloquium on Theoretical Aspects of Computing (ICTAC 2018),
415--434.
%
\bibitem{STS19} R. Senda, Y. Takata and H. Seki,
Generalized register context-free grammars,
13th Int. Conf. Language and Automata Theory and Applications (LATA 2019), 259--271,
revised version: IEICE Trans. Inf. \& Syst., E103-D(3), 540--548, 2020.

\bibitem{STS21} R. Senda, Y. Takata and H. Seki,
Forward regularity preservation property of register pushdown systems,
IEICE Trans. Inf. \& Syst., E104-D(3), 370--380, 2021.

\bibitem{ST12}
F. Song and T. Touili, Pushdown model checking for malware detection,
TACAS 2012, extended version:
Int. J. Softw. Tools. Tehchnol. Transfer 16, 147--173, 2014.

\bibitem{Tz10} N. Tzevelekos, Fresh-register automata,
36th ACM Annual Symp. on Principles of Programming Languages (POPL 2009), 295--306.

\bibitem{Wa96} I. Walukiewicz, Pushdown processes: Games and model-checking,
Pushdown processes: Games and model checking,
8th Int. Conf. on Computer Aided Verification (CAV 1996),
%8th International Conference on Computer Aided Verification,
62--74, revised version:
Inform. Comput. 164, 234--263, 2001.

\bibitem{XO13}
C. Xiaojuan and M. Ogawa,
Well-structured extensions of pushdown systems,
24th Int. Conf. on Concurrency Theory (CONCUR 2013),
121--136.

%\bibitem{Fi13} B. Finkbeiner and S. Schewe, Bounded synthesis,
%Int. J. Softw. Tools. Tehchnol. Transfer 15, 519--539, 2013.
%\bibitem{NTS01}
%N. Nitta, Y. Takata and H. Seki,
%An efficient security verification method for programs with stack inspection,
%ACM CCS,
%%8th ACM Conference on Computer and Communications Security,
%68--77, 2001.
%
% \bibitem{AHV95}
% S. Abiteboul, R. Hull and V. Vianu,
% Foundations of Databases, Part D: Datalog and Recursion,
% Addison-Wesley, 1995.
%
% \bibitem{BDMSS09} % [9] of RPQd
% M. Boja\'{n}czyk, C. David, A. Muscholl, T. Schwentick and L. Segoufin,
% Two-variable logic on data trees and XML reasoning,
% Journal of the ACM 56(3), 2009.
%
% \bibitem{CGP01}
% E. M. Clarke, O. Grumberg and D. A. Peled, Model checking. MIT Press, 2001.
%
% \bibitem{CS81} % [1]
% A. K. Chandra and L. J. Stockmeyer,
% Alternation,
% 17th Annual Symposium on Foundations of Computer Science (FOCS 1976),
% also in: Journal of the ACM, 28, 114-133, 1981.
%
% \bibitem{Fi10} % [5] of Figueira and Segoufin 2011
% D. Figueira,
% Forward-XPath and extended register automata on data-trees,
% International Conference on Database Theory (ICDT 2010).
%
% \bibitem{Fi12} % [25] of WRA
% D. Figueira,
% Alternating register automata on finite data words and trees,
% Logical Methods in Computer Science 8(1:22), 1--43, 2012.
%
% \bibitem{FS11} % [21] of RPQd
% D. Figueira and L. Segoufin,
% Bottom-up automata on data trees and vertical XPath,
% 28th Symposium on Theoretical Aspects of Computer Science (STACS 2011), 93--104.
%
% \bibitem{JK07} % [12] of Figueira and Segoufin 2011
% M. Jurdzi\'{n}ski and R. Lazi\'{c},
% Alternation-free modal mu-calculus for data trees,
% Logic in Computer Science (LICS 2007).
%
% \bibitem{KNSK94}
% Y. Kaji, R. Nakanishi, H. Seki and T. Kasami,
% The computational complexity of the universal recognition problem
% for parallel multiple context-free grammars,
% Computational Intelligence, 10(4), 440--452, 1994.
%
% \bibitem{KT08} % [5]
% M. Kaminsky and T. Tan,
% Tree automata over infinite alphabets,
% Pillars of Computer Science 2008, LNCS 4800, 386--423.
%
% \bibitem{Li04}
% L. Libkin,
% Elements of Finite Model Theory, Chapter 10: Fixed Point Logics and Complexity Classes,
% Springer, 2004.
%
% \bibitem{LMV16} % [6]
% L. Libkin and W. Martens and D. Vrgo\v{c},
% Querying graphs with data,
% Journal of the ACM 63(2), 14:1--14:53, 2016.
%
% \bibitem{MSV00} % pebble automata
% T. Milo, D. Suciu and V. Vianu,
% Type checking for XML transformers,
% 19th ACM Symposium on Principles of Database Systems, 11--22, 2000.
% %
% %
% \bibitem{SI00} % [9]
% H. Sakamoto and D. Ikeda,
% Intractability of decision problems for finite-memory automata,
% Theoretical Computer Science 231, 297--308, 2000.
%

\end{thebibliography}
